%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Integrated Master's Degree in Electronic Engineering} % Degree
    {University of Leeds} % Institution
    {} % Location
    {2012-2016} % Date(s)
    {
      % Achieved Upper-Second Class Honours in an Electronic Engineering integrated Masters Degree.
      \begin{cvitems}
          \item{Masters Level Embedded Systems Module covering implementation of embedded systems on an ARM A9 processor using Eclipse for DS5. Also developed a modular/portable graphical user interface library, exhibited through a multiplayer curve drawing game. Demonstrated high proficiency in C, in depth understanding of ARM Assembly/Toolchain, technical writing.}
          \item{Individual Project involved the parameterised simulation of Valve Amplifier in MATLAB for use as a creative audio effect. Demonstrated Non-linear and linear DSP, analogue circuit analysis, mathematical modelling, presentation and exhibition skills.}
          \item{Embedded Systems Project produced a prototype calculator capable of evaluating strings containing multiple embedded brackets and floating point values. Developed in the ARM Keil MDK for a Tiva C Microcontroller (ARM Cortex-M4).}
          %\item{Embedded system design: C programming, circuit and PSU design, PCB layout. Undertook a project using an arduino and a small LCD to create a standalone Gameboy style toy loaded with the classic game Snake. PSU design, PCB layout, embedded programming.}
          \item{Communications and Network Security Module: OSI 7-Layer Model, TCP/IP structure, Error control methods, Flow control. Network security projects to trace and analyse a TLS handshake, then to model and hack a low order public key encryption algorithm.}
          \item{Digital Communications: Physical layer engineering principles, Digital Modulation schemes, Optical communications Receivers for binary communication systems, Lab project to examined receiver techniques and BER for BPSK, QPSK and QAM.}
          %\item{Group Design Project consisted of designing and building a modular synthesizer in a team of 4. Personally achieved design and prototype build of versatile Voltage Controlled Oscillator; complex circuit design/development, testing/fault finding, project management.}
          \item{Mobile Applications Project: (Objective C) Created a resistor combinations calculator for iOS using the first fit decreasing algorithm.}
          %\item{Other modules covered; Circuit Analysis \& Design, Analytical Techniques, Semiconductor Physics, DSP for Communications, Control Systems, Industry Studies.}
      \end{cvitems}
    }

  \cventry
    {A-Level Results} % Degree
    {Collyers Sixth Form} % Institution
    {} % Location
    {2010-2012} % Date(s)
    {
      \begin{cvitems}
        \item Electronics A* , Physics A, Maths A, Music Technology B
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
