%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Senior Embedded Software Engineer}
    {Pod Point}
    {}
    {Jan '23 - March '25}
    { 
      Demonstrated extensive technical ability and excellent interpersonal skills in a highly-skilled team developing Smart EV-Chargers. Undertook several important roles as the team moved from maintaining maintaining legacy products into a full platform redesign and subsequent launch to market.
      \begin{cvitems}
        \item{Migrated Eclipse based project to command-line build system for enhanced automation.}
        \item{In close collaboration with hardware, developed a DC current detection algorithm with effective aliasing suppression for HF noise.}
        \item{Played an active and vocal role in the architecture of safety-critical MCU subsystem for the new platform. Leveraging and further developing my expertise in FreeRTOS.}
        \item{Implemented a modular signal processing pipeline for fault detection/monitoring alongside delivering many core components for the MCU subsystem.}
        \item{Built upon existing debug skills, expanding further into hardware issues and gaining experience debugging in an embedded linux context.}
        \item{Led the embedded systems contribution to product compliance. Undertook complicated cross-discipline investigations and subsequently implemented algorithms to exceed stringent regulations.}
        \item{Coordinated the design, implementation and deployment of automated system testing infrastructure:}
        \begin{cvitems}
          \item{Developed a pytest based test suite capable of executing the same tests in both a hardware and software context.}
          \item{Integrated the tests into github workflows which included self-hosted runner deployments.}
          \item{Facilitated the remote development of hardware tests, providing invaluable resource to a hybrid team.}
        \end{cvitems}
      \end{cvitems}  
    }

  % \cventry
  %   {Senior Embedded Software Engineer}
  %   {Pod Point}
  %   {}
  %   {Jan '23 - March '25}
  %   { 
  %     Played a key role in development of the safety-critical microcontroller subsystem as part of a full platform re-implementation. Led the embedded systems contributions to compliance in close collaboration with the hardware team. And went on to manage the design and deployment of automated test infrastructure.
  %     \begin{cvitems}
  %       \item{Architected core components of the safety controller’s multi-threaded design, leveraging my expertise in FreeRTOS}
  %       \item{Focussed on implementing thread-safe peripheral drivers for the safety controller.}
  %       \item{Assisted with debugging in all aspects of the project; from hardware issues up to application level issues in an embedded linux context.}
  %       \item{Led on most DSP aspects of the firmware, including a redesign of the pipeline to represent signals in the complex domain.}
  %       \item{Undertook complicated investigations as part of the compliance process and subsequently implemented algorithms to meet stringent regulations.}
  %       \item{Architected and implemented automated system testing infrastructure:}
  %       \begin{cvitems}
  %         \item{Developed a pytest based test suite capable of executing the same tests in both a hardware and software context.}
  %         \item{Integrated the tests into github workflows which included self-hosted runner deployments.}
  %         \item{Facilitated the remote development of hardware tests, providing invaluable resource to a hybrid team.}
  %       \end{cvitems}
  %     \end{cvitems}  
  %   }

  \cventry
    {Senior Embedded Software Engineer}
    {Sportable}
    {}
    {Nov '19 - Oct '22}
    {
      Worked in a small team to develop a wireless 3D tracking technology for the realtime collection of sports data. Joined the company 
      at an early stage of development, oversaw the succesful release of the product to market and acheived promotion to senior level.
      \begin{cvitems}
        \item{Worked with a complicated embedded stack that widened the scope of my coding ability. The stack our team maintained is comprised of 4 applications:}
        \begin{cvitems}
          \item{Server Side application to offload data from the network over USB and aggregate, process and publish data streams for cloud connections.}
          \item{FreeRTOS application on the wireless device to manage the device state and collect sensor data.}
          \item{Bare-metal application optimised to control the radio IC and manage connection to the TDMA network.}
          \item{Python based integration, production and unit testing framework - which I took a lead role in design and implementation of.}
        \end{cvitems}
        \item{Gained experience in a fast-paced and dynamic start-up environment. Improving my ability to write flexible code to handle rapidly changing and evolving specifications.}
        \item{Trained and supervised the junior engineers, whilst also leading the development of coding practices that create a more approachable stack for new starters.}
        \item{Developed the skills necessary to work with wireless networks. Putting these into practice by designing and building tools that aided debugging of wireless devices.}
      \end{cvitems}  
    }

  \cventry
    {Embedded and DSP Engineer}
    {Meridian Audio Limited}
    {}
    {Aug '17 - Nov '19}
    {
      Starting at Meridian as a purely embedded firmware engineer then after about 6 months my role was expanded to include DSP software development.
      \begin{cvitems}
        \item{Developed, maintained and tested high quality code for both MCU and DSP architectures. Integrating new hardware, extending feature set for new products, tuning and developing DSP algorithms.}
        % \item{General duties were to maintain and improve existing codebases. Integrating new hardware, extending feature set for new products, tuning and developing DSP algorithms.}
        \item{The overarching project during my time at meridian was the design and implementation of a multi-product hardware and software development platform:}
        \begin{cvitems}
          \item{Worked with senior engineers to realise a forward compatible system design. }
          \item{Researched and realised the toolchain and development environment to speed development and increase collaboration.}
          \item{Established both MCU and DSP codebases for the project, transferring over existing functionality and re-implementing when necessary. Prioritising SOLID principles and acheiving a highly flexible structure to handle multiple platforms/products.}
          \item{Specific projects included; asynchronous multirate input/output audio framework for SHARC, drivers for SPI and UART for MCU, Polyphase Filter module, Model-View-Controller implementation, Guaranteed delivery communication protocol.}
          \item{Eventually took on a leading role, orchestrating the firmware aspects of the project between a small team of developers.}
        \end{cvitems}
        % \item{Played an important role in the design of a multi-product hardware and software development platform. Established both the MCU and the DSP codebases for this project, transferring existing functionality to the new platform with a focus on documentation and improved structure for continuous integration.}
        % \item{Responsible for the research and realisation of entire toolchain and development tools/environment for the new platform, focusing both on ease of development and delivery to production.}
        \item{Driving force in the release of a multi-award winning product, working across departments to ensure the outcome was both engineered to the highest standard but also realised the brief on a restricted timescale.}
        \item{Worked with a colleague to bring in a code review process using Gitea which was subsequently adopted across all new projects in the department.}
        % \item{Took a lead role in generating consensus around working practices in new platforms and brought in a code review process to go with this.}
      \end{cvitems} 
    }

    \cventry
      {Embedded Software Engineer}
      {Caldertech}
      {}
      {June '17 - Aug '17}
      {Developed an SD Card driver library to integrate with an open source filesystem. Working on a platform in the very early stages of development and delivering a fully functioning library to the client with associated documentation and a handover session to compliment regular code reviews.}

%---------------------------------------------------------
\end{cventries}
