%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Additional Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Principal Engineer} % Affiliation/role
    {\texttt{rayDance}} % Organization/group
    {Various} % Location
    {2016 - PRESENT} % Date(s)
    {
      Long running passion project developing an effective sound-to-light algorithm and platform based around an STM32F7.
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed a fully asynchronous DMX receiver to provide an interface capable of professional integration.}
        \item {Complex signal processing pipeline utilising DTFT, IIR/FIR implementations from the CMSIS-DSP library and some custom algorithms.}
        \item {Python simulation of the same pipeline to aid in debug and development of the algorithm.}
        \item {High-speed asynchronous LED driver suitable for scaling to variable LED arrays.}
        \item {Prototype hardware platform that was successfully demonstrated at Amsterdam Dance Event in 2023.}
      \end{cvitems}
    }

    \cventry
    {Co-Owner}
    {Groundforce Soundsystem}
    {Leeds}
    {2012 - 2018}
    {Designed and built a small (yet mighty!) sound system in Leeds to hire out for parties, and events.
    \begin{cvitems}
        \item Researched and developed designs for loudspeaker enclosures, using programs like winISD to simulate designs.
        \item Practical end-user experience of Digital Signal Processing for Audio.
        \item Repaired broken equipment; amplifiers, mixers, turntables.
        \item Managed bookings, logistics and finances for the business.
        \item System is now set to be installed at a community centre in London, providing an asset to teach young people about live sound.
    \end{cvitems}
    }

    % \cventry
    % {Test Technician}
    % {Etrac}
    % {Guildford}
    % {2008 - 2012}
    % {Tested and repaired a variety of electronic and electrical components for clients from the railway industry. Including some clerical work.
    % \begin{itemize}
    %     \item Vast experience of fault finding, with a good knowledge of test procedures.
    %     \item Responsible for revising test and repair procedures in preparation for an external audit.
    %     \item Often worked alone, prioritising and organising my time accordingly.
    % \end{itemize}}

%---------------------------------------------------------
\end{cventries}
